Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2017-10-11 paper.tex
Added description for cost-sensitive methods

@@

>>>>

This method adjusts the classifier's prediction output by changing its probability threshold which depends on a predefined cost.  To illustrate the idea of the cost-sensitive classification, the threshold $P$ for a given case can be calculated based on a general cost matrix $C$, where $C$ can be represented as given in Equation \ref{Eq:costMatrix}.

\begin{equation}
C=\left[\begin{array}{cc}
0 & \lambda\\
\mu & 0
\end{array}\right]
\label{Eq:costMatrix}
\end{equation}

Based on the matrix $C$, the threshold $P$ can be determined using Equation \ref{Eq:costThreshold}.

\begin{equation}
P=\frac{\mu}{\mu+\lambda}
\label{Eq:costThreshold}
\end{equation}

Therefore, $P$ can be used to distinguish between the two classes. If the probability classification output of the model is less than the threshold then it classifies as the minority class, otherwise it classifies as a majority class.

@@

In this method, a given classification algorithm performs the learning process based on a new version of the dataset, where the instances are re-weighted internally according to some predefined costs.
